---
title: "Individual Assignment"
output:
  html_document: default
  pdf_document: default
---
#### (a)
```{r}
set.seed(6)
X=rnorm(100)
set.seed(2)
noise=rnorm(100)
```

#### (b)
```{r}
Y=1+2*X+3*X^2+4*X^3+noise
```

#### (c)
```{r}
library(leaps)
data=data.frame(Y,X)
regfit.full=regsubsets(Y~poly(X,10,raw=T),data,nvmax=10)
reg.summary=summary(regfit.full)

# CP
which.min(reg.summary$cp)
plot(reg.summary$cp,xlab = "Number of Predictors",main="CP",type="l")
points(3,reg.summary$cp[3],col="red",cex=2,pch=20)
coef(regfit.full,3)

# BIC
which.min(reg.summary$bic)
plot(reg.summary$bic,xlab = "Number of Predictors",main="BIC",type="l")
points(3,reg.summary$bic[3],col="red",cex=2,pch=20)
coef(regfit.full,3)

# ADJR2
which.max(reg.summary$adjr2)
plot(reg.summary$adjr2,xlab = "Number of Predictors",main="Adjusted R^2",type="l")
points(7,reg.summary$adjr2[7],col="red",cex=2,pch=20)
coef(regfit.full,7)
```
##### According to CP, the best model is the model with three predictors: y=0.9+2*x+3*x^2+4*x^3

##### According to BIC, the best model is the model with three predictors: y=0.9+2*x+3*x^2+4*x^3

##### According to ADJR2, the best model is the model with seven predictors: y=0.7+2*x+6*x^2+4*x^3-4*x^4+2*x^6-0.3*x^8+0.02*x^10

#### (d)
```{r}
# Forward Selection
regfit.fwd=regsubsets(Y~poly(X,10,raw=T),data,nvmax=10,method="forward")
reg.fwd.summary=summary(regfit.fwd)

#CP
which.min(reg.fwd.summary$cp)
plot(reg.fwd.summary$cp,xlab = "Number of Predictors",main="CP",type="l")
points(3,reg.fwd.summary$cp[3],col="red",cex=2,pch=20)
coef(regfit.fwd,3)

## BIC
which.min(reg.fwd.summary$bic)
plot(reg.fwd.summary$bic,xlab = "Number of Predictors",main="BIC",type="l")
points(3,reg.fwd.summary$bic[3],col="red",cex=2,pch=20)
coef(regfit.fwd,3)

# adjr2
which.max(reg.fwd.summary$adjr2)
plot(reg.fwd.summary$adjr2,xlab = "Number of Predictors",main="Adjusted R^2",type="l")
points(10,reg.fwd.summary$adjr2[10],col="red",cex=2,pch=20)
coef(regfit.fwd,10)
```
##### According to CP, the best model is the model with three predictors: y=0.9+2*x+3*x^2+4*x^3

##### According to BIC, the best model is the model with three predictors: y=0.9+2*x+3*x^2+4*x^3

##### According to ADJR2, the best model is the model with ten predictors: y=0.7+2*X+5*X^2+5*X^3-3*X^4-2*X^5+2*X^6+0.8*X^7-0.5*X^8-0.1*X^9+0.05*X^10
```{r}
# Backward Selection
regfit.bwd=regsubsets(Y~poly(X,10,raw=T),data,nvmax=10,method="backward")
reg.bwd.summary=summary(regfit.bwd)
#cp
which.min(reg.bwd.summary$cp)
plot(reg.bwd.summary$cp,xlab = "Number of Predictors",main="CP",type="l")
points(3,reg.bwd.summary$cp[3],col="red",cex=2,pch=20)
coef(regfit.bwd,3)

## BIC
which.min(reg.bwd.summary$bic)
plot(reg.bwd.summary$bic,xlab = "Number of Predictors",main="BIC",type="l")
points(3,reg.bwd.summary$bic[3],col="red",cex=2,pch=20)
coef(regfit.bwd,3)

# adjr2
which.max(reg.bwd.summary$adjr2)
plot(reg.bwd.summary$adjr2,xlab = "Number of Predictors",main="Adjusted R^2",type="l")
points(7,reg.bwd.summary$adjr2[7],col="red",cex=2,pch=20)
coef(regfit.bwd,7)
```
##### According to CP, the best model is the model with three predictors: y=0.9+2*x+3*x^2+4*x^3

##### According to BIC, the best model is the model with three predictors: y=0.9+2*x+3*x^2+4*x^3

##### According to ADJR2, the best model is the model with seven predictors: y=0.7+2.18*X+5.6*X^2+3.9*X^3-3.6*X^4+1.7*X^6-0.3*X^8+0.02*X^10  

##### By comparing those results, we can see that those three ways can not always choose the same best model. 

