---
title: "Module1 Individual Assignment 0901"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
###(a)
library(MASS)
?Boston
dim(Boston)
fix(Boston)
```

### The cloumns represent the 14 features of Housing Values in Suburbs of Boston, and the rows represent there are 506 housing values in suburbs of BOston.

```{r}
###(b)
pairs(Boston)
```

### The nox and age has a positive correlation.

### The indus and dis has a negative correlation.

```{r}
###(c)
attach(Boston)
plot(crim~zn+indus+chas+nox+rm+age+dis+rad+tax+ptratio+black+lstat+medv)
```

### The higher proportion of owner-occupied units built prior to 1940, the higher rate of crim.

### The closer distances to Boston employment centres, the higher rate of crim.

### The lower median value of owner-occupied homes, the higher rate of crim.

```{r}
###(d)
attach(Boston)
hist(crim,breaks=20)
range(crim)
hist(tax,breaks=20)
range(tax)
hist(ptratio,breaks=20)
range(ptratio)
```

### Only few of the suburbs(nearly 100 surburbs) have a higher crime rate(over 5).Range:0.00632 to 88.97620

### Over 100 surburbs of Boston have a higher tax rate(more than 600). Range:187 to 711

### Over 200 surburbs of Boston have a higher pupil-teacher ratio by town(over 20).Range: 12.6 to 22

```{r}
###(e)
attach(Boston)
sum(chas==1)
```

### There are 35 suburbs bound the Charles river.

```{r}
###(f)
median(ptratio)
```

### The median pupil-teacher ratio among the towns is 19.05.

```{r}
###(g)
library(dplyr)
Arranged_medv=arrange(Boston,medv)
head(Arranged_medv,1)
summary(Boston)
```

### The suburb that has the lowest medv is shown abrove.

### Compared to the overall ranges for those predictors:

### crime: above the 3rd quartile;

### zn: no residential land zoned for lots over 25,000 sq.ft.;

### indus: at the 3rd quartile;

### chas: not bound river

### nox: above 3rd quartile;

### rm: below 1st quartile;

### age: at max;

### dis: below 1st quartile;

### rad: at max;

### tax: at 3rd quartile;

### ptratio: at 3rd quartile;

### black: at max;

### lstat: above 3rd quartile.

```{r}
###(h)
sum(rm>7)
sum(rm>8)
summary(subset(Boston,rm>8))
```

### The suburbs with more than 8 rooms per dwelling have a lower crime rate, a higher tax, a higher lstat and a lower medv.
